Spatial Analysis of Russian Law Firms Naming

### 2024-07-17 law-firms-names/Paper.Rmd
Write a paragraph about firm names and their connection with geography, #4

>>>>

Geographical research of services may focus on a variety of subjects. Some classical pathways of such research include analysis of centers and systems of service or of consumers' behavior, needs and demands, including estimation of influencing factors, investigation on the actual level of services provision, applied scientific work related to the management of social infrastructure [@Tkachenko2016]. Studies of firm names, sometimes also referred to as company names, brand names or just brands, is relatively unusual yet potentially fruitful method in the geography of services. Firm names are designed to distinguish the business from the competitors, to make an emphasis on the field of activity or its geographical area, inform about services supplied by a provider and corresponding benefits. Having these functions, brands convey a substantial portion of information in a short text message. Such information may be useful to discover the city's business landscape and consumer's perception of a particular city with its characteristic services [@Raento2001], analyze the trends common to a specific industry in a region [@Marjavaara2022] or the role of place as reflected in the toponyms in the business development and consumer attitudes [@Peluso2012; @Zhang2014; @Erdogan2016; @Noorda2019]. Company names represent the characteristics of businesses and thus may act as “meta-proxy” for a bulk of intertwined economic metrics. Such a complex nature makes them suitable for regions identification, especially in the case of vernacular regions [@Reed1976; @Liesch2015; @Vukosav2016; @Holtkamp2018]. Other interactions between places and brands, e.g. the contribution of commercial branding to place branding [@Florek2013] or its compliance with the latter [@BassolsiGardella2023] may also be of interest.
